Understanding the Landscape of Childlessness in the U.S.: A Data-Driven Exploration (1972-2022)

### 2024-03-11 outputs/paper/paper.qmd
new updates on formatting

Structurally, in @sec-intro, our paper starts with a brief dissection of the nature of childlessness in America and the contributing factors. Subsequently, in @sec-data and @sec-result, we talk about the nature of the data obtained and analyze the results garnered from the data with suitable tables and charts. Next, @sec-discussion provides further insights and future areas of study. Finally, @sec-data concludes and summarizes our main findings. To complete the paper, @sec-appendix clarifies how each variable within each dataset is measured.

@@

# Result and Analysis {#sec-result}

@fig-nochild-age illustrates @tbl-nochild-age, which shows a consistent rise in childlessness across all age groups in the United States from 1972 to 2022.

@@

@fig-nochild-class visualizes @tbl-nochild-class which depicts the gradual increase in the percentage of childless individuals across four social classes (Lower Class, Working Class, Middle Class, Upper Class) in the United States from 1972 to 2022. The graph reveals an upward trend in childlessness for all classes over the five decades.

@@

@fig-nochild-degree visualization of @tbl-nochild-degree, presents a comparative analysis of childlessness across individuals with different levels of educational attainment (Less than High School, High School and College's Degree or Higher) in the United States from 1972 to 2022. The graph utilizes line trends to depict the percentage of childless individuals within each degree category over the five decades.

@@

Overall, the data illustrates an increase in childlessness accross all health levels and conditions approaching 2022. As mentioned, people with excellent health has the highest percentage of childlessness, having a 10.49% increase throughout the 50-year period (28.26% in 1972 to 38.75% in 2022). People with good and fair health exhibit similar rate of childlessness in 2022, at about 30%. In particular, people with fair health markedHowever, people with poor health, once having the lowest rate of childlessness (at 12.27% in 1972), now increases to 20.40% in 2022, which translates to a substantial 8.13% increase.

@@

The data demonstrates that a significant portion of people who have never married are childless. However, more and more people are reluctant to get married but still consider having children. This is observable in the childlessness percentage decrease of people who never marry, decreasing from 96.73% in 1972 to 72.53% in 2022. For people who are divorced, separated and widowed, this percentage flucatuates, displaying the complex dynamics between these relationship status and childbearing. For married people though, this childlessness percentage also decreases, from 10.51% in 1972 to 13.97% in 2022. This again demonstrates the overall decrease of childbirths due to varying factors.

>>>>

Structurally, in [Introduction], our paper starts with a brief dissection of the nature of childlessness in America and the contributing factors. Subsequently, in [Data] and [Result], we talk about the nature of the data obtained and analyze the results garnered from the data with suitable tables and charts. Next, [Discussion] provides further insights and future areas of study. Finally, [Conclusion] concludes and summarizes our main findings. To complete the paper, [Appendix] clarifies how each variable within each dataset is measured.

@@

# Result {#sec-result}

@fig-nochild-age shows a consistent rise in childlessness across all age groups in the United States from 1972 to 2022.

@@

@fig-nochild-class depicts the gradual increase in the percentage of childless individuals across four social classes (Lower Class, Working Class, Middle Class, Upper Class) in the United States from 1972 to 2022. The graph reveals an upward trend in childlessness for all classes over the five decades.

@@

@fig-nochild-degree presents a comparative analysis of childlessness across individuals with different levels of educational attainment (Less than High School, High School and College's Degree or Higher) in the United States from 1972 to 2022. The graph utilizes line trends to depict the percentage of childless individuals within each degree category over the five decades.

@@

Overall, the data shows an increase in childlessness across all health levels and conditions approaching 2022. As mentioned, people with excellent health has the highest percentage of childlessness, having a 10.49% increase throughout the 50-year period (28.26% in 1972 to 38.75% in 2022). People with good and fair health exhibit similar rate of childlessness in 2022, at about 30%. In particular, people with fair health markedHowever, people with poor health, once having the lowest rate of childlessness (at 12.27% in 1972), now increases to 20.40% in 2022, which translates to a substantial 8.13% increase.

@@

The data demonstrates that a significant portion of people who have never married are childless. However, more and more people are reluctant to get married but still consider having children. This is observable in the childlessness percentage decrease of people who never marry, decreasing from 96.73% in 1972 to 72.53% in 2022. For people who are divorced, separated and widowed, this percentage fluctuates, displaying the complex dynamics between these relationship status and childbearing. For married people though, this childlessness percentage also decreases, from 10.51% in 1972 to 13.97% in 2022.
